---
title: "Correct kilometer"
author: "sergey"
date: "April 25, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r source files, echo=FALSE}
source("./R/ML_utils.R")
source("./R/data-clean.R")
library(ggplot2)
```

## Data overview
```{r , echo=FALSE}
ggplot(autoData(), aes(yearOfRegistration, kilometer))+
  geom_count() +
  scale_size_area() +
  geom_smooth()
```

Trend line seems unlikely, as it seems there's no correlation that the older autos have more kilometers.  
The number of cars with less or one year old and more than 70000 km is abnormal.
```{r, echo=FALSE}
ggplot(autoData()[autoData()$yearOfRegistration > 2009,], 
       aes(yearOfRegistration, kilometer)) +
  geom_count() +
  scale_size_area()
```

To calculate a true regression line or trend line, we create the next subset of a data:
- skip the whole year-2016-data as it looks abnormal
- skip the data, where the majority of km is 150000. As there's no values >150000 km, we're not able to distinguish between 150K and 250K. We'll take the subset in that years, where 150000km doesn't have a big share of observations.
That's 2011 - 2015 period:
```{r, echo=FALSE}
ggplot(autoData()[autoData()$yearOfRegistration > 2008, ], 
       aes(yearOfRegistration, kilometer)) +
  geom_count(aes(size = ..prop.., group = yearOfRegistration)) +
  scale_size_area(max_size = 10)
```

```{r, echo=FALSE}
subData <- autoData()[autoData()$yearOfRegistration > 2010 & 
                        autoData()$yearOfRegistration < 2016, 
                      c("yearOfRegistration", "kilometer")]
qplot(data = subData, x = yearOfRegistration, y = kilometer) + geom_smooth(method = "gam")
```

```{r}
kmFit <- lm(data = subData, kilometer ~ yearOfRegistration)
qplot(y = predict.lm(kmFit), x = subData$yearOfRegistration)
```

